Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Given a graph $G = (V,E)$ for triangle detection, we will construct an instance of the 3D 3-SJ problem with input size $3m$. W.l.o.g., let us assume that each vertex of $V$ is represented as a unique integer in $[|V|]$. Initialize $R_1, R_2$, and $R_3$ as 3 empty sets of rectangles. For each edge $\set{u, v}\in E$ where $u < v$, we add
\begin{itemize}
    \item a rectangle $(-\infty, \infty) \times [u,u] \times [v,v]$ to $R_1$;
    \item $[v,v] \times(-\infty, \infty)\times [u,u]$ to $R_2$;
    \item $[v,v] \times [u,u] \times(-\infty, \infty) $ to $R_3$.
\end{itemize}
Note that every rectangle in $R_1$ (resp., $R_2$ and $R_3$) has $(-\infty, \infty)$ as the x- (resp., y- and z-) projection.

@@

    \item Conversely, consider that $\J(R_1, R_2, R_3)$ is non-empty. Consider an arbitrary result tuple $(r_1, r_2, r_3) \in \J(R_1, R_2, R_3)$. Assume, w.l.o.g., that $r_1 = (-\infty, \infty) \times [u, u] \times [v, v]$.
    Because the z-projection of $r_2$ must match that of $r_1$, we assert that $r_2$ must have the form $[w, w] \times (-\infty, \infty) \times [v, v]$ where $w > u$. Because the x-projection of $r_3$ must match that of $r_2$ and the y-projection of $r_3$ must match that of $r_1$, it follows that $r_3$ must have the form $[w, w] \times [u, u] \times (-\infty, \infty)$. This means that the edges $\set{u,v}$, $\set{v,w}$, and $\set{u,w}$ must all exist in $G$, and thus form a triangle.
}

>>>>

Given a graph $G = (V,E)$ for triangle detection, we will construct an instance of the 3D 3-SJ problem with input size $3m$. W.l.o.g., let us assume that each vertex of $V$ is represented as a unique integer in $[|V|]$. Initialize $R_1, R_2$, and $R_3$ as 3 empty sets of rectangles. For each edge $\set{u, v}\in E$ where $u < v$, we add
\begin{itemize}
    \item a rectangle $(-\infty, \infty) \times [u,u] \times [v,v]$ to $R_1$;
    \item a rectangle $[v,v] \times(-\infty, \infty)\times [u,u]$ to $R_2$;
    \item a rectangle $[v,v] \times [u,u] \times(-\infty, \infty) $ to $R_3$.
\end{itemize}
Note that every rectangle in $R_1$ (resp., $R_2$ and $R_3$) has $(-\infty, \infty)$ as the x- (resp., y- and z-) projection.

@@

    \item Conversely, consider that $\J(R_1, R_2, R_3)$ is non-empty. Consider an arbitrary result tuple $(r_1, r_2, r_3) \in \J(R_1, R_2, R_3)$. Assume, w.l.o.g., that $r_1 = (-\infty, \infty) \times [u, u] \times [v, v]$.
    Because the z-projection of $r_2$ must match that of $r_1$, we assert that $r_2$ must have the form $[w, w] \times (-\infty, \infty) \times [v, v]$ for some $w > u$. Because the x-projection of $r_3$ must match that of $r_2$ and the y-projection of $r_3$ must match that of $r_1$, it follows that $r_3$ must have the form $[w, w] \times [u, u] \times (-\infty, \infty)$. This means that the edges $\set{u,v}$, $\set{v,w}$, and $\set{u,w}$ must all exist in $G$, and thus form a triangle.
}
